\documentclass[12]{article}


\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=1.25in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[document]{ragged2e}
\usepackage[parfill]{parskip}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}

\titleformat{\section}[frame]
{ \huge}
{ }
{ .25em}
{ \filcenter\bfseries\lowercase}


\titleformat{\subsection}
{\bfseries\Large}
{ \hspace{-.25in}$\bullet$}
{ 0em}
{ }


\titleformat{\subsubsection}[runin]
{ \bfseries}
{ }
{ -.75em}
{ } [---]

\titlespacing{\subsubsection}
{0em}{.25em}{1em}

\renewcommand{\maketitle}{
\begin{center}
{\huge\bfseries
\theauthor} 

\vspace{.25em}

jeppefaerch1@gmail.com --- +45 42665237

\end{center}
}


\begin{document}

\title{R\'esum\'e}
\author{Jeppe Færch}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Technical Skills}

\subsection{Languages}

\subsubsection{Programming}

C\#, C++ .

\subsubsection{Scripting}

Bash, Python, R, SQL.

\subsubsection{Markup}

 HTML, {\LaTeX},  RMarkdown.

\subsection{Client software}

\subsubsection{Operating system}

Microsoft Windows, Linux (Unix-like).

\subsubsection{Desktop applications}

Adobe Creative Cloud, Microsoft Office,  RStudio, TeXMaker.

\subsection{Multimedia}

\subsubsection{Image}

Most adept volleying between GIMP and Photoshop, otherwise InDesign, Illustrator.

\subsubsection{Video}

I use Blender or Premiere Pro for video sequencing. Open Broadcaster Service (OBS) \\ and ShareX for screencasting and basic operations, respectively.

\subsubsection{Audio}

Audacity for basic audio manipulation. Also familiar with music production software like LMMS.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}

\subsection{BSc in  Mathematics-Economics (in progress)}

at the University of Copenhagen (UCPH), August 2020 - 

\subsection{HTX in Communication/IT A, Programming B}
at Viden Djurs Game College, August 2017 - June 2020

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Job Experience}

\subsection{Kitchen Staff : October 2018 - June 2020.}

Campus Djursland, Region Midtjylland.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Voluntary Service}

\subsection{Student Council 2019 - 2020}
at VID Gymnasier Grenaa.

\subsection{Student assistant and tutoring 2017 - 2020}
various conferences at VID Gymnasier Grenaa / Game College.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{GitHub}

For more information about my GitHub click on the following link:
\href{https://github.com/peachypit}{\\ https://github.com/peachypit}


\end{document}